---
title: "County-Level Analysis"
author: "Mikaela Renaud-Lowther"
date: "2024-11-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load necessary packages

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```


## Importing two csv files

```{r}
salesdata <- read.csv("project.sales.counties.csv")
ACSdata <- read.csv("project.acs.counties.csv")
```

## Creating Average Sales Data by County 

```{r}
avgsalesdata <- salesdata %>%
  group_by(county) %>%
  summarize(avgsalesdollars = mean(sale.dollars), 
            avgsalesvolume = mean(sale.volume))
```

## Creating a single data frame

```{r}
countydata <- merge(ACSdata, avgsalesdata, by = "county")

attach(countydata)
```

## Initial regression model

```{r}
model1 <- lm(avgsalesdollars ~ income, data = countydata)

summary(model1)
```
## Assessing which controls to add to the model - controls must be correlated with income and have an effect on avgsalesdollars

```{r}
cor(income, high.school)
cor(income, bachelor)
cor(income, unemployment)
```
 
## Adding high.school and unemployment to the model as controls

```{r}
model2 <- lm(avgsalesdollars ~ income + high.school + unemployment, data = countydata)

summary(model2)
```

## Incorporating race into the model 

```{r}
countydata <- countydata %>%
  mutate(percentwhite = pop.white/population)
```

```{r}
model3 <- lm(avgsalesdollars ~ income + high.school + unemployment + percentwhite, data = countydata)

summary(model3)
```

## Adding an interaction term between income and percentwhite 

```{r}
model4 <- lm(avgsalesdollars ~ income + high.school + unemployment + percentwhite +income*percentwhite, data = countydata)

summary(model4)
```

```{r}
ggplot(countydata, aes(x = income, y = avgsalesdollars)) +
  geom_point() +
  ggtitle("Income ($) vs. Average Annual Sales ($)") +
  xlab("Income ($)") +
  ylab("Average Annual Sales")
```

